---
title: "Survey Report"
author: "Marcos Abreu"
format: html
# revealjs
editor: visual
---

## Evaluation of Survey Results

During the P6W4 and P7W1 weeks it was conducted a survey with the Value Stream associates and temporary workers and the maintenance team.

This presentation brings the analysis of the survey results.

## Responses

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(readxl)
library(janitor)
library(patchwork)

source("R/survey_read_data.R")
source("R/survey_plot.R")

folder = "/Users/marcos.abreu/workspace/survey-mars/data"
survey_data <- readSurveyMonkeyData(folder, "Java - Feedback.xlsx")

extra_columns <- 
  survey_data |> 
  select(`Onde você atua?`,
         `Qual seu turno?`,
         `Qual seu tipo de contrato?`) |> 
  names()
names(extra_columns) <- c('linha', 'turno', 'contrato')

dist_df <- get_respondent_data(survey_data, extra_columns)

plot_linha <- 
  dist_df |> plot_survey_by(linha)
plot_turno <- 
  dist_df |> plot_survey_by(turno)
plot_contrato <- 
  dist_df |> plot_survey_by(contrato)

plot <- ((plot_linha+ggtitle("")) + (plot_turno+ggtitle(""))) / (plot_contrato+ggtitle("")+coord_flip()) 
plot + plot_annotation(
  title = 'Number of answers',
  subtitle = 'Status 2023-06-22',
  caption = 'Disclaimer: partial data'
)
```

## Survey Summary

Summary of collected answers:

```{r}
#| echo: false
#| warning: false
#| message: false

plot_all_likert_data(survey_data)



```

## Measured Dimensions

::: columns
::: {.column width="50%"}
-   Awareness

    -   Vision

    -   Perception of the Change

    -   Communication
:::

::: {.column width="50%"}
-   Desire

    -   Leadership

    -   Engagement

    -   Intention

        -   Attitudes

        -   Perceived Norms

        -   Self-Capacity
:::
:::

The following slides show results by different dimensions

```{r}
#| echo: false
#| warning: false
#| message: false

# Groups of questions:
cat_vision <- c("Q01", "Q02")
cat_change_management <- c("Q03", "Q04")

cat_communication <- c("Q05", "Q06")

cat_attitude <- c("Q07", "Q08")

cat_leadership <- c("Q09", "Q10")
cat_engagement <- c("Q11", "Q12")

cat_perceived_norms <- c("Q13", "Q14")
cat_self_efficacy <- c("Q15")

```

## Vision

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, cat_vision)
```

## Perception of Change Management

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, cat_change_management)
```

## Communication

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, cat_communication)
```

## Leadership

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, cat_leadership)
```

## Engagement

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, cat_engagement)
```

## Behavior

```{r}
#| echo: false
#| warning: false
#| message: false
#| 
plot_likert_by(survey_data, c(cat_attitude, cat_perceived_norms, cat_self_efficacy))
```

Vamos avaliar por grupo de linha, turno, contrato.
